Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-27 manuscript/manuscript.tex
more outline to materials and methods

\subsection*{Influenza hemagglutinin sequences.}
We downloaded all full-length protein-coding sequences for each of the 18 influenza HA subtypes. 
We used \texttt{phydms\_prepalignment} \citep{hilton2017phydms} to filter and align the sequences. 
We subsampled to five per year plus the required sequences.

>>>>

\subsection*{Influenza hemagglutinin sequences.}
We downloaded all full-length protein-coding sequences for each of the 18 influenza HA subtypes. 
We used \texttt{phydms\_prepalignment} \citep{hilton2017phydms} to filter and align the sequences. 
We subsampled to five per year plus the required sequences. 
Total of 87 sequences. 
Inferred tree topology using \texttt{RAxML}.

\subsection*{Simulations.}
How was the model fit? 
How many simulations? 
How was the tree constructed?

\subsection*{Expected Asymptotic Sequence Identity.}
How were the models fit? 
What is the equation? 
What is the equation for the $\omega_r$ term? (does it include the ExpCM $\omega$?)
How is the GY94$\omega_r$ model constructed? ie How does it interact with the $\omega$ value in the GY94 model?

\subsection*{Deep mutational scanning amino acid preferences.}
Where did we get the preferences? 
How were the average preferences calculated? 
How was the ``hybrid" sequence made? 
Numbering scheme.
